Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-13 paper/sheaf_lics.tex
minor changes on xy definitions

\usepackage{enumerate}
\usepackage{wasysym}
\usepackage[all]{xy}
\def\dar[#1]{\ar@<2pt>[#1]\ar@<-2pt>[#1]} %double arrows in xy
\def\tar[#1]{\ar@<2pt>[#1]\ar@<0pt>[#1]\ar@<-2pt>[#1]} %triple arrows in xy
\DeclareMathOperator{\Type}{Type}
\DeclareMathOperator{\HProp}{HProp}
\DeclareMathOperator{\IsHProp}{IsHProp}
\DeclareMathOperator{\nat}{nat}
\DeclareMathOperator{\Unit}{Unit}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Contr}{Contr}
\DeclareMathOperator{\IsContr}{IsContr}
\newcommand{\IsType}[1]{\mathrm{Is-}#1\mathrm{-type}}
\newcommand{\modal}{\ensuremath{\ocircle}}

@@

In homotopy type theory, we have 
$$X\times_Y \cdots\times_Y X = \sum_{x:X^n} (f x_1 = f x_2) \land
\cdots \land (f x_{n-1} = f x_n).$$
\begin{defi}
  If $f:X \to Y$ is a map, then the {\em \v{C}ech nerve} of $f$ is the
  diagram
  $$\xymatrix{
    C(f) := \cdots~ X \times_Y X \times_Y X \tar[r] & X \times_Y X \dar[r] & X
  }$$
with canonical projections.
\end{defi}

@@

We now need to show that $\square$ is universal. The following
lemma is central in the proof~:
\begin{lem}\label{lem:sepiscolim}
  Let $T:\Type_{n+1}$. Then $\square T$ is the colimit of the closed
  diagonal diagram
  $$\xymatrix{ 
    \cdots \overline{\Delta_3} \tar[r] & \overline{\Delta_2} \dar[r] &
    \overline{\Delta_1}
  }$$
where $\Delta_k$ is the $k$-pullback of $\id : T \to T$.
\end{lem}

@@

Now, let $Q$ be a separated $\Type_{n+1}$, and $f:T \to Q$. Then the
following diagram commutes
$$\xymatrix{ 
    \cdots \overline{\Delta_3} \tar[r] \ar[rd]_{f\circ \pi_1} & \overline{\Delta_2}
    \dar[r] \ar[d]^{f\circ \pi_1} &
    \overline{\Delta_1} = T \ar[ld]^{f\circ \pi_1}\\
    & Q &
  }$$
But we know (lemma~\ref{lem:sepiscolim}) that $\square T$ is the
colimit of the closed diagonals diagram, thus there is an universal
arrow $\square T \to Q$.

@@

Let $f,g$ be two maps from $\sum_{e:E} (\chi\,e)$ to $\sum_{x:A}
(Bx)$, equal when precomposed with $\pi_1$.
$$\xymatrix{
  \sum_{e:E} (\chi\, e) \dar[r]^{f\circ\pi_1}_{g\circ \pi_1} \ar[d]_{\mathrm{dense}}& \sum_{x :A} (Bx) \\
  E \dar[ru]^f_g&
}$$
We can restrict the previous diagram to 
$$\xymatrix{
  \sum_{e:E} (\chi\, e) \dar[rr]^{\pi_1\circ f\circ\pi_1}_{\pi\circ g\circ \pi_1} \ar[d]_{\mathrm{dense}}&& A \\
  E \dar[rru]^{\pi_1\circ f}_{\pi_1\circ g}&
},$$ 
and as $A$ is separated, $\pi_1\circ f = \pi_2 \circ g$.
For the second components, let $x:E$. Notice that for all $x:E$,
$\sum_{y:E} x = y$ has a dense subobject, $\sum_{y:\sum_{e:E} (\chi\,
  e)} x=y_1$~:

$$\xymatrix{
  \sum_{y:\sum_{e:E} (\chi\,
  e)} x=y_1 \dar[rrr]^{\pi_2\circ f\circ\pi_1\circ \pi_1}_{\pi_2\circ g\circ \pi_1\circ \pi_1} \ar[d]_{\mathrm{dense}}&&& B\,x \\
  \sum_{y:E} x = y \dar[rrru]^{\pi_2\circ f\circ \pi_1}_{\pi_2\circ g\circ \pi_1}&
}$$
Using the sepatation property of $B\,x$, one can show that second
components, transported correctly along the first components equality,
are equal. The complete proof can be found in the formalisation.
This proves the following proposition
\begin{prop}
  $(\square,\mu)$ defines a modality on $\Type_{n+1}$.
\end{prop}

>>>>

\usepackage{enumerate}
\usepackage{wasysym}
\usepackage[all]{xy}
\def\dar[#1]#2{\ar@<-#2>[#1]\ar@<#2>[#1]} %double arrows in xy
\def\tar[#1]#2{\ar@<#2>[#1]\ar@<0pt>[#1]\ar@<-#2>[#1]} %triple arrows in xy
\DeclareMathOperator{\Type}{Type}
\DeclareMathOperator{\HProp}{HProp}
\DeclareMathOperator{\IsHProp}{IsHProp}
\DeclareMathOperator{\nat}{nat}
\DeclareMathOperator{\Unit}{Unit}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Contr}{Contr}
\DeclareMathOperator{\IsContr}{IsContr}

\def\mymathhyphen{{\hbox{-}}}

\newcommand{\IsType}[1]{\mathrm{Is\mymathhyphen}#1\mathrm{\mymathhyphen
    type}}
\newcommand{\modal}{\ensuremath{\ocircle}}

@@

In homotopy type theory, we have 
$$X\times_Y \cdots\times_Y X = \sum_{x:X^n} (f x_1 = f x_2) \land
\cdots \land (f x_{n-1} = f x_n).$$
\begin{defi}
  If $f:X \to Y$ is a map, then the {\em \v{C}ech nerve} of $f$ is the
  diagram
  $$\xymatrix{
    C(f) := \cdots~ X \times_Y X \times_Y X \tar[r]{4pt} & X \times_Y X \dar[r]{2pt} & X
  }$$
with canonical projections.
\end{defi}

@@

We now need to show that $\square$ is universal. The following
lemma is central in the proof~:
\begin{lem}\label{lem:sepiscolim}
  Let $T:\Type_{n+1}$. Then $\square T$ is the colimit of the closed
  diagonal diagram
  $$\xymatrix @C=4em  { 
    \cdots \overline{\Delta_3} \tar[r]{4pt} & \overline{\Delta_2} \dar[r]{2pt} &
    \overline{\Delta_1}
  }$$
where $\Delta_k$ is the $k$-pullback of $\id : T \to T$.
\end{lem}

@@

Now, let $Q$ be a separated $\Type_{n+1}$, and $f:T \to Q$. Then the
following diagram commutes
$$\xymatrix @C=4em{ 
    \cdots \overline{\Delta_3} \tar[r]{4pt} \ar[rd]_{f\circ \pi_1} & \overline{\Delta_2}
    \dar[r]{2pt} \ar[d]^{f\circ \pi_1} &
    \overline{\Delta_1} = T \ar[ld]^{f\circ \pi_1}\\
    & Q &
  }$$
But we know (lemma~\ref{lem:sepiscolim}) that $\square T$ is the
colimit of the closed diagonals diagram, thus there is an universal
arrow $\square T \to Q$.

@@

Let $f,g$ be two maps from $\sum_{e:E} (\chi\,e)$ to $\sum_{x:A}
(Bx)$, equal when precomposed with $\pi_1$.
$$\xymatrix @R=4em @C=4em{
  \sum_{e:E} (\chi\, e) \ar@<-2pt>[r]_{g\circ\pi_1} \ar@<2pt>[r]^{f\circ \pi_1} \ar[d]_{\mathrm{dense}}& \sum_{x :A} (Bx) \\
  E \ar@<-2pt>[ru]_{g} \ar@<2pt>[ru]^{f}&
}$$
We can restrict the previous diagram to 
$$\xymatrix @R=4em @C=5em{
  \sum_{e:E} (\chi\, e) \ar@<-2pt>[r]_{\pi_1\circ g\circ\pi_1} \ar@<2pt>[r]^{\pi_1\circ f\circ \pi_1} \ar[d]_{\mathrm{dense}}& \sum_{x :A} (Bx) \\
  E \ar@<-2pt>[ru]_{\pi_1\circ g} \ar@<2pt>[ru]^{\pi_1\circ f}&
}$$
and as $A$ is separated, $\pi_1\circ f = \pi_2 \circ g$.
For the second components, let $x:E$. Notice that for all $x:E$,
$\sum_{y:E} x = y$ has a dense subobject, $\sum_{y:\sum_{e:E} (\chi\,
  e)} x=y_1$~:

$$\xymatrix{
  \sum_{y:\sum_{e:E} (\chi\,
  e)} x=y_1 \dar[rrr]{2pt}^{\pi_2\circ f\circ\pi_1\circ \pi_1}_{\pi_2\circ g\circ \pi_1\circ \pi_1} \ar[d]_{\mathrm{dense}}&&& B\,x \\
  \sum_{y:E} x = y \dar[rrru]{2pt}^{\pi_2\circ f\circ \pi_1}_{\pi_2\circ g\circ \pi_1}&
}$$
Using the sepatation property of $B\,x$, one can show that second
components, transported correctly along the first components equality,
are equal. The complete proof can be found in the formalisation.
This proves the following proposition
\begin{prop}
  $(\square,\mu)$ defines a modality on $\Type_{n+1}$.
\end{prop}
